Nondeterministic Bigraphical Reactive Systems for Markov Decision Processes\thanks{Supported by organization x.}

### 2018-08-15 paper.tex
Introduction

\providecommand\longrightarrowRHD{\relbar\joinrel\relbar\joinrel\mathrel\RHD}
\providecommand\longrightarrowrhd{\relbar\joinrel\relbar\joinrel\mathrel\rhd}
\providecommand\longrightdoublearrowRHD{\mathrel\LHD\joinrel\relbar\joinrel\relbar\joinrel\mathrel\RHD}

\makeatletter
\providecommand*\xrightarrowRHD[2][]{\ext@arrow 0055{\arrowfill@\relbar\relbar\longrightarrowRHD}{#1}{#2}}
\providecommand*\xrightarrowrhd[2][]{\ext@arrow 0055{\arrowfill@\relbar\relbar\longrightarrowrhd}{#1}{#2}}
\makeatother

@@

TODO: introduction to bigraphs and everything else
%Bigraphical reactive systems (BRS) \cite{DBLP:books/daglib/0022395} are a
%universal formalism for modelling interacting systems that evolve in time and
%space.

@@

\begin{figure}
  \centering
  \begin{minipage}{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{models/pbrs_example/take_lhs.pdf}
  \end{minipage}
  $\longrightdoublearrowRHD$
  \begin{minipage}{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{models/pbrs_example/take_rhs.pdf}
  \end{minipage}
  \caption{The reaction rule to take an \texttt{Object} from a
    \texttt{Location}.}
  \label{pbrs_rule}
\end{figure}

@@

\section{A Case Study in Autonomous Agents}

@@

\begin{figure}
  \centering
  \begin{minipage}{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{models/agent2/goIn_lhs.pdf}
  \end{minipage}
  $\longrightdoublearrowRHD$
  \begin{minipage}{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{models/agent2/goIn_rhs.pdf}
  \end{minipage}
  \caption{Left to right: the reaction rule to go inside; right to left: the
    reaction rule to go outside.}
  \label{go_in_out}
\end{figure}

>>>>

\providecommand\longrightarrowRHD{\relbar\joinrel\relbar\joinrel\mathrel\RHD}
\providecommand\longrightarrowrhd{\relbar\joinrel\relbar\joinrel\mathrel\rhd}
\providecommand\longdoublearrowRHD{\mathrel\LHD\joinrel\relbar\joinrel\relbar\joinrel\mathrel\RHD}

\makeatletter
\providecommand*\xrightarrowRHD[2][]{\ext@arrow 0055{\arrowfill@\relbar\relbar\longrightarrowRHD}{#1}{#2}}
\providecommand*\xrightarrowrhd[2][]{\ext@arrow 0055{\arrowfill@\relbar\relbar\longrightarrowrhd}{#1}{#2}}
\providecommand*\xdoublearrowRHD[2][]{\ext@arrow 0055{\arrowfill@\relbar\relbar\longdoublearrowRHD}{#1}{#2}}

\makeatother

@@

Bigraphical reactive systems (BRS) \cite{DBLP:books/daglib/0022395} are a
universal formalism for modelling interacting systems that evolve in time and
space. They consist of bigraphs and reaction rules. Bigraphs are algebraic terms
for modelling agents, connections, and their placement within each other, while
reaction rules specify how one bigraph can evolve into another. BRSs have
been used to represent a diverse range of phenomena: games
\cite{DBLP:journals/tochi/BenfordCRS16}, network management
\cite{DBLP:journals/scp/CalderKSS14}, protocols
\cite{DBLP:journals/fac/CalderS14}, biological processes
\cite{DBLP:journals/entcs/KrivineMT08}, real world environments
\cite{DBLP:conf/giscience/WaltonW12}, etc. Extending BRSs with probabilities,
uncertainty, and rewards allows us to model an even wider range of processes and
systems, examples of which will be given in Section \ref{case_study}. In this
section we introduce and define the main concepts built upon in the remainder of
paper: Markov decision processes and BRSs.

@@

\begin{figure}
  \centering
  \begin{minipage}{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{models/pbrs_example/take_lhs.pdf}
  \end{minipage}
  $\xrightarrowRHD{1}$
  \begin{minipage}{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{models/pbrs_example/take_rhs.pdf}
  \end{minipage}
  \caption{The reaction rule to take an \texttt{Object} from a
    \texttt{Location}.}
  \label{pbrs_rule}
\end{figure}

@@

\section{A Case Study in Autonomous Agents} \label{case_study}

@@

\begin{figure}
  \centering
  \begin{minipage}{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{models/agent2/goIn_lhs.pdf}
  \end{minipage}
  $\xdoublearrowRHD{1}$
  \begin{minipage}{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{models/agent2/goIn_rhs.pdf}
  \end{minipage}
  \caption{Left to right: the reaction rule to go inside; right to left: the
    reaction rule to go outside.}
  \label{go_in_out}
\end{figure}
